Msc Thesis Figures

### 2020-08-06 docs/msc_thesis_figures.Rmd
fix rmd

```{r message=TRUE, warning=TRUE}
source('~/Documents/Master/Thesis/land_con_monteregie/scripts/functions/draw_scenario.R')
for (scenario in c(39, 42, 45, 48, 51)){
  the_plot <- draw_scenario(scenario, mxp = mxp)
  the_name <- paste0("scenario_", as.character(scenario),"_compare.png")
  ggsave(plot = the_plot, 
         filename = paste0("../thesis/figures/",the_name), width = 20, height = 10, dpi = the_dpi)
}

>>>>

```{r message=FALSE, warning=FALSE}
source('../scripts/functions/draw_scenario.R')
for (scenario in c(39, 42, 45, 48, 51)){
  the_plot <- draw_scenario(scenario, mxp = mxp)
  the_name <- paste0("scenario_", as.character(scenario),"_compare.png")
  ggsave(plot = the_plot, 
         filename = paste0("../thesis/figures/",the_name), width = 30, height = 12, dpi = the_dpi)
}
